\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-11-20 article.tex
testBranches.R revisions

\subsection{Interactive plotting functions}
\label{interaction}

@@

We would like to state that users can still hard code one or two variables in the \code{plotPathOnAll()} function, even with the \code{animate} option set to a value of ``TRUE". The first call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis. When hovering over labels, the label name and yield value is revealed. The second call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis and development year on the vertical axis. When hoering over labels, the label name, yield value, and development year is revealed.

@@

>>>>

\section{Interactive plotting functions}
\label{interaction}

@@

We would like to state that users can still hard code one or two variables in the \code{plotPathOnAll()} function, even with the \code{animate} option set to a value of ``TRUE". The first call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis. When hovering over labels, the label name and yield value is revealed. The second call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis and development year on the vertical axis. When hovering over labels, the label name, yield value, and development year is revealed.

@@

\section{Branch calculations and parsings}

It may be helpful for users to search through the descendant branches of an individual of interest to compare and contrast how a variable of interest changes within these branches. For instance, which descending branches of a particular soybean variety are producing the highest yields? Which are developing new varieties in recent years? Which descending branches of a particular academic statistician have large proportions of individuals graduating from a certain school or country? What propotion have thesis titles containing a word of interest? Which are graduating new students in recent years?
